---
title       : Reverberation and Energy Policy in the United States
subtitle    : Do federal policies reverberate in regional prices
author      : Emma Heffernan and Devvart Poddar
framework   : revealjs        # {io2012, html5slides, shower, dzslides, ...}
revealjs    :
 transition: linear
 center: "false"
highlighter : highlight.js  # {highlight.js, prettify, highlight}
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- .bg

<!-- Loading Required packages -->
``` {r loadpackages, echo = FALSE, results = "hide", message=FALSE, warning=FALSE}
load <- c("dplyr", "magrittr", "ggplot2", "plm", "rio", "slidify", "slidifyLibraries", "lubridate", "gganimate", "tm", "koRpus", "stringi")

lapply(load, require, character.only = T)
```

<!-- Refering to a different stylesheet-->
<head>
  <link rel="stylesheet" href="assets/css/white.css">
</head>

<!-- Front Page -->
## Reverberation and Energy Policy in the United States
<br> <br> <br> <br> <br>

<small>Emma Heffernan & Devvart Poddar</small>

---

## Introduction
<br>

<ul style="list-style-type:square" class="wrapper">
  <li>
    <small>
      Rising electricity costs in developed nations has become the political topic <i>du jour</i>
      across OECD jurisdictions. The cost of electricity matters: the impact of rising electricity
      costs is felt most acutely by low-income individuals
    </small>
  </li>
  <br>
  <li class="fragment">
    <small>
      Much of the blame for rising electricity prices has been levied against government
      renewable energy policies
    </small>
  </li>
  <br>
  <li class="fragment">
    <small>
      We argue that as the federal energy court gives more legitimacy to renewable
      energy policies and goals, this increased legitimacy will result in the implementation
      of more renewable energy policies in states.
    </small>
  </li>
</ul>

--- &vertical

## Theoretical Framework
<br>

<ul style="list-style-type:square" class="wrapper">
  <li>
    <small>
      Robert Putnam (1988): <b>Two-level games</b>. Theorises the concept of reverberation; <i>"lnternational pressures can
      reverberate within domestic politics”</i>  subsequently altering the
      position of domestic civic society groups
    </small>
  </li>
  <br>
  <li class="fragment">
    <small>
      We will use a modified version of this theory to model how the federal and state spheres interact in the United States
    </small>
  </li>
  <br>
  <li class="fragment">
    <small>
      ADD IMAGE HERE
    </small>
  </li>
</ul>

--- &vertical

## Data & Method
<br>

<ul style="list-style-type:square" class="wrapper">
  <li>
    <small>
      Data sourced from multiple web sources. We get data on renewable electricity prices
      from EIA for all states (except Hawaii) and for a time period of 15 years
    </small>
  </li>
  <br>
  <li class="fragment">
    <small>
      We use the presence of Renewable Portfolio Standards (RPS) using data from <thead>
      study by <b>WHO AGAIN</b>?
      </thead>
    </small>
  </li>
  <br>
  <li class="fragment">
    <small>
      Finally we measure federal level policies in terms of their enforcement and focus on
      renewable energy standards. We get this from the Federal Energy Regulatory Commission
      (FERC) for 2001 onwards.
    </small>
  </li>
</ul>

***

### Seasonal Trend in Prices;

```{r pricetrend, echo = FALSE}
prices.data <- import("./Output/processed data/mergeddata.csv") %>%
  mutate(time = ymd(paste0(year, "-", month, "-01"))) %>%
  group_by(time) %>%
  summarise(mean = mean(Prices)) %>%
  mutate(year = year(time)) %>%
  as.data.frame()
```
``` {r plottrend, echo = FALSE, fig.align='center', fig.show="animate", interval=0.3, warning = FALSE, cache = 2, out.width="", message=FALSE}
p <- ggplot(prices.data) +
  geom_line(aes(time, mean, group = 1, frame = year, cumulative = T)) +
  labs(y = "Electricity Prices", title = "Year; ") +
  scale_x_date(date_breaks = "1 year", date_labels = "%Y") +
  scale_y_continuous(breaks = 7:13) +
  theme_bw() +
  theme(
    axis.title.x = element_blank()
  )

gg_animate(p)

```

***

### Distilling Text

<small> <b>What it looks like before;</b> </small>

<div class="fragment">

  ```{r before, echo=FALSE, results="asis"}

  text <- "10. The Tribe argues that PacifiCorp is not taking action to obtain water quality
  certification and thus is not diligently pursuing its license application.8
   The Tribe
  therefore asks the Commission to dismiss the relicense application and require the
  company to file a plan to decommission the project.9
  11. We agree with the Tribe that the circumstances of this case are far from ideal.
  As noted above, Commission staff issued the EIS in November 2007. The Commission
  could act on PacifiCorp’s application but for the absence of water quality certification.10
  The Klamath Project is operating under the terms of the 1954 license, and, as a result, the
  many environmental benefits that could accrue under the new license have not
  occurred.11 Under the express terms of the Clean Water Act, however, the Commission "

format_text <- paste("<p style='text-align:justify;'> <small>",
                     text, "</small> </p>")

cat(format_text)
  ```
</div>

<small> <b>What it looks like after; </b> </small>

<div class="fragment">

``` {r after, echo = F, results = "asis"}
text.clean <- function(text) {
  text <- as.character(text)

  # Defining extra words
  extra.words <- c("united", "states", "america", "pdf", "ferc")

  # Removing stop words, punctation, numbers, special charcters and whitespace
  text %<>%
    stri_replace_all_regex("[[:punct:]]|\\$|\\+", "") %>%
    stri_replace_all_regex("\\s+", " ") %>%
    VectorSource() %>%
    VCorpus() %>%
    tm_map(content_transformer(tolower)) %>%
    tm_map(removeNumbers) %>%
    tm_map(removeWords, stopwords()) %>%
    tm_map(removeWords, extra.words) %>%
    # sapply(`[`, "content") %>%
    sapply(as.character)

  return(text)
}

# Lemmatising text to convert to tokens
text.lemma <- function(text) {
  text <- as.character(text) %>%
    tolower()

  # Create a lemma dataframe of the text
  ## Creating a temporary file
  file.con <- file("temp.txt")
  writeLines(text, file.con)
  close(file.con)

  # Creating temporary dataframe with lemma
  temp.data <- treetag("temp.txt",
    treetagger = "manual",
    lang = "en",
    TT.options = list(
      path = "/home/devvart/treetagger",
      preset = "en"
      ))

  temp.data <- temp.data@TT.res %>%
    select(token, lemma) %>%
    mutate(
      lemma = ifelse(lemma == "<unknown>", token, lemma)
      )

  file.remove("temp.txt")

  # Replacing words with their lemma
  for (x in 1:nrow(temp.data)) {
    # Values
    token <- paste0("\\b", temp.data$token[x], "\\b")
    # token <- temp.data$token[x]
    lemma <- temp.data$lemma[x]

    # Replacing
    error <- try(text %<>% stri_replace_all_regex(token, lemma))

    if (inherits(error, "try-error")) {
      message.text <- paste0(token, " ----- ", lemma)
      message(message.text)
      stop("Stopping cleaning until error resolves")
    }
  }

  # Removing text spaces
  text %<>% stri_replace_all_regex("\\s+", " ")

  return(text)
}

new_text <- text %>%
  text.clean() %>%
  text.lemma()

format_text <- paste("<p style='text-align:justify;'> <small>",
                     new_text, "</small> </p>")

cat(format_text)
```

</div>

--- &vertical

## Variables; A snapshot
 <br>

``` {r summarytable, echo = FALSE, results = "asis"}
load.data <- import("./Output/processed data/mergeddata.csv") %>%
  mutate(context_30 = context_30 * 100,
         order.ave = order.ave * 100,
         renewable.ave = renewable.ave * 100) %>%
  select(Prices, RPS, Electric, order.ave, renewable.ave, context_30, temperature)

summary.func <- function(x) {
  c(Mean = mean(x, na.rm = T),
    Median = median(x, na.rm = T),
    Min = min(x, na.rm = T),
    Max = max(x, na.rm = T)
  )
}

tablecode <- function(df, tabletype="gridtable"){
  tmp <- noquote(apply(df, 1, function(x) paste0("<td style='text-align:center' data-th='", sprintf("%s",colnames(df)), "'>", x, "</td>", collapse=" ")))

  cat(
  c(
  noquote(paste0("<table id='", tabletype,"' style='width:100% text-align:center;'> ")),
  noquote(paste0("<tr>", paste0("<th>", sprintf("%s",colnames(df)), "</th>", collapse=" "), "</tr>")),
  noquote(unlist(lapply(tmp, function(x) paste0("<tr'>", x, "</tr>")))),
  noquote("</table>")
  )
  )
}

summary.table <- sapply(load.data, summary.func) %>%
  round(2) %>%
  as.data.frame() %>%
  mutate(Description = rownames(.)) %>%
  select(Description, everything())

des.table <- data.frame(
  a = c("Unit", "Source"),
  b = c("$", "<a href=https://www.eia.gov/>EIA</a>"),
  c = c(" ", " "),
  d = c(" ", " "),
  e= c("% point", "<a href=https://ferc.gov/>FERC</a> (text)"),
  f = c("% point", "<a href=https://ferc.gov/>FERC</a> (text)"),
  g = c("% point", "<a href=https://ferc.gov/>FERC</a> (text)"),
  h = c(" ", " ")
)

colnames(summary.table) <- c("  ", "Prices", "RPS", "Deregulation",
                             "Freq. of Order", "Freq. of Renewable",
                             "Context; Renewable", "Temperature")

colnames(des.table) <-  c("  ", "Prices", "RPS", "Deregulation",
                             "Freq. of Order", "Freq. of Renewable",
                             "Context; Renewable", "Temperature")

summary.table %<>%
  rbind(des.table)

tablecode(summary.table, tabletype = "minimal")
```
<br><br><br><br>
<small style="font-size:0.5em;"> <b>Note:</b> CSS sourced from <a href="https://github.com/psych-git/psych-git.github.io">psych-git</a></small>


--- &vertical

## Results
 <br>

--- &vertical

## Discussion
<br>

<script type="text/javascript">
  Reveal.configure({ slideNumber: true });
</script>
